\rule{\textwidth}{2pt}\\[0.5cm] \textbf{Payout profile approximation with vanilla European options}\\[0.5cm] \rule{\textwidth}{1pt}

### 2025-02-02 src/article.tex
formatting

\title{\rule{\textwidth}{1pt}\\[0.5cm]
Payout profile approximation with vanilla European options\\[0.5cm]
\rule{\textwidth}{1pt}}
\author{\small Vlad Kochetov \\ \small Faculty of Mechanics and Mathematics, \\ \small Taras Shevchenko National University of Kyiv \\ \small \texttt{vladkoch@knu.ua}}
\date{\today}

@@

\keywords{Vanilla options, payout profile, financial engineering, option pricing, approximation}

>>>>

\title{\rule{\textwidth}{2pt}\\[0.5cm]
\textbf{Payout profile approximation with vanilla European options}\\[0.5cm]
\rule{\textwidth}{1pt}}
\author{\small \textbf{Vlad Kochetov} \\
    \small Faculty of Mechanics and Mathematics, \\
    \small Taras Shevchenko National University of Kyiv \\
    \small \texttt{vladkoch@knu.ua}
}
\date{\today}

@@

\keywords{Vanilla Options, 
          Payout Profile, 
          Financial Engineering, 
          Option Pricing, 
          Approximation,
          Numerical Methods}
